---
title: "Getting Started with binomial"
author: "Ray Yuan"
date: "5/3/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  error = TRUE
)
```

```{r setup}
library(binomial)
```
## Binomial Package Description

This binomial package allows you to create binomial random variables and plot them, as well as provides many helper functions to compute statistics for binomial distributions

## Creating a b.r.v

We first create a brv with the `bin_variable` function:
```{r}
brv <- bin_variable(5, 0.2)
brv
```

Use the `summary` function to get a summary of your newly created brv
```{r}
summary(brv)
```

## Binomial r.v. Distributions and Visualizations


#### regular distributions and cumulative distributions
Use the `bin_distribution` function to create a b.r.v object of type bindis
```{r}
dis_reg <- bin_distribution(5, 0.2)
dis_reg
```
Use the `bin_cumulative` function to create a bincum object
```{r}
dis_cum <- bin_cumulative(5, 0.3)
dis_cum
```

For visualization, we can use the `plot` function 
```{r}
plot(dis_reg)
plot(dis_cum)
```


## Other Useful Functions for computing statistics of Binomial Distributions

#### bin_choose
n choose k
```{r}
bin_choose(3, 2)
```

#### bin_probability
gets probability of a # successes in # trials with a probability "prob"

```{r}
bin_probability(success = 3, trials = 5, prob = 0.2)
```

#### bin_mean
mean of a binomial random variable.
```{r}
bin_mean(5, 0.2)
```

#### bin_variance
variance of a binomial random variable
```{r}
bin_variance(5, 0.2)
```

#### bin_mode
mode of a binomial random variable.
```{r}
bin_mode(5, 0.2)
```

#### bin_skewness
skewness of a binomial random variable.
```{r}
bin_skewness(5, 0.2)
```

#### bin_kurtosis
kurtosis of a binomial random variable.
```{r}
bin_kurtosis(5, 0.2)
```
