---
title: "Getting Started with binomial"
author: "Ray Yuan"
date: "5/3/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  error = TRUE
)
```

```{r setup}
library(binomial)
```
## Binomial

This binomial package is designed to simulate binomial random variables and provide statistics and visualizations for success rates given a number of trials and probability of success. 

## Creation of Binomial Random Variable Objects
A simple way to view basic statistics about a binomial random variable distribution is to create an instance of a binomial random variable object (`bin_variable`) and then simply print out that object. 

We define a binomial random variable as `bin_variable(trials, probability of success)`:
```{r}
rv <- bin_variable(10, 0.3)
```

If we print out the binomial random variable object, we see its input trials and probability of success:
```{r}
rv
```

We can see useful statistics about a random variable's distribution by using the `summary()` function
```{r}
rv_summary <- summary(rv)
rv_summary
```

## Distributions of Binomial Random Variables
We can also create probability of success distributions using the functions `bin_distribution` and `bin_cumulative`, which return `bindis` and `bindcum` objects respectively. 

#### bin_distribution
We create a `bindis` object representing a distribution of a binomial random variable using the function `bin_distribution(trials, probability of success)`:
```{r}
dis <- bin_distribution(5, 0.3)
class(dis)
```

Printing out a binomial distribution prints a `data.frame` of the distribution:
```{r}
dis
```

We can plot this binomial distribution using the `plot()` function:
```{r, fig.show='hold'}
plot(dis)
```

#### bin_cumulative
In addition to creating the probability of success distributions, we can also create a distribution that calculates the probability of having less than or equal to a number of successes using `bin_cumulative`.

We create a `bincum` object using the function `bin_cumulative(trials, probability of success)`
```{r}
dis2 <- bin_cumulative(5, 0.3)
class(dis2)
```

Printing out the distribution prints a `data.frame` of the distribution:
```{r}
dis2
```

We can plot the running success probability of this binomial distribution using the `plot()` function:
```{r, fig.show='hold'}
plot(dis2)
```

## Other Binomial Random Variable Functions

#### bin_choose
Function that returns n choose k. `bin_choose(n, k)`:
```{r}
bin_choose(5, 2)
bin_choose(5, 1:5)
bin_choose(5, 6)
```

#### bin_probability
Function that returns the probability of achieving a certain number of successes in a binomial random variable. `bin_probability(number of successes, trials, probability of success)`
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
bin_probability(success = 0:2, trials = 5, prob = 0.5)
bin_probability(success = 6, trials = 5, prob = 0.5)
bin_probability(success = 0:5 , trials = 5, prob = 0.5)
```

## Summary Measure Functions
The package also includes a numerous number of summary measure functions which give individual statistics about a binomial random variable.

#### bin_mean
Returns the mean of a binomial random variable
```{r}
bin_mean(10, 0.3)
```

#### bin_variance
Returns the variance of a binomial random variable
```{r}
bin_variance(10, 0.3)
```

#### bin_mode
Returns the mode of a binomial random variable
```{r}
bin_mode(10, 0.3)
```

#### bin_skewness
Returns the skewness of a binomial random variable
```{r}
bin_skewness(10, 0.3)
```

#### bin_kurtosis
Returns the kurtosis of a binomial random variable
```{r}
bin_kurtosis(10, 0.3)
```
